Enforced Invariant Confluence

### 2018-04-30 doc/paper/sections/invariant_confluence.tex
Fixed weird example 1.

\begin{example}\examplelabel{Ints}
  $O = (\ints, +)$ is a distributed object consisting of integers merged by
  addition; $t(x) = x + 1$ is a transaction which adds one to a state; and
  $\setst{x \in \ints}{x \geq 0}$ is the invariant that states $x$ are
  non-negative.
\end{example}

>>>>

\begin{example}\examplelabel{Ints}
  $O = (\ints, \max)$ is a distributed object consisting of integers merged by
  $\max$; $t(x) = x + 1$ is a transaction which adds one to a state; and
  $\setst{x \in \ints}{x \geq 0}$ is the invariant that states $x$ are
  non-negative.
\end{example}
